Making all equalities equal

### 2021-09-21 paper.lagda.tex
organized the code

\begin{code}
module Equalities {a ℓ} {A : Set a} where
  ≣-Type' = ≣-Type {a} {ℓ} {A}

  module _
    (_≡₁_ : ≣-Type')
    (_≡₂_ : ≣-Type')
    ⦃ eq₁ : IsEquality {a} {ℓ} _≡₁_ ⦄
    ⦃ eq₂ : IsEquality _≡₂_ ⦄
    where

    ℓ₁ = ℓ-max a ℓ

    record IsEquality₂ (_≣_ : ≣-Type') : Set (ℓ-suc (ℓ-max a ℓ)) where
      constructor eq
      field
        ≣-≡-≡ : ∀ {x y} → let
          x≡y : Type ℓ₁
          x≡y = x ≡₁ y

@@

@@

      record IsEquality₃ (_≣_ : ≣-Type') : Set (ℓ-suc (ℓ-max a ℓ)) where
        constructor eq
        field
          ≣-≡-≡ : ∀ {x y} → let
            x≡y : Type ℓ₁
            x≡y = x ≡₁ y

@@

      instance
        ≡₂-Equality₃ : IsEquality₃ _≡₂_
        ≡₂-Equality₃ = eq α
          where
            open IsEquality eq₃
            α : ∀ {x y} → (x ≡₂ y) ≡₃ (x ≡₁ y)
            α = transport ≡-≡-≣ (IsEquality₂.≣-≡-≡ ≡₂-Equality₂)

      module _ {_≣_ : ≣-Type'} where
        sym-Equality₃ : (≡-≡-≣ : {x y : A} → let
          x≡y : Type (ℓ-max a ℓ)
          x≡y = x ≡₁ y
          x≣y = x ≣ y
          in x≡y ≡₃ x≣y)
          → IsEquality₃ _≣_
        sym-Equality₃ ≡-≡-≣ = eq (let
          α₁ = IsEquality.≡-≡-≣ eq₃
          α₂ = transport (sym α₁) ≡-≡-≣
          in transport α₁ (sym α₂))

\end{code}

>>>>

\begin{code}
module Equalities {a ℓ} {A : Set a} where
  ≣-Type' = ≣-Type {a} {ℓ} {A}
  ℓ₁ = ℓ-max a ℓ

  module _
    (_≡₁_ : ≣-Type')
    ⦃ eq₁ : IsEquality {a} {ℓ} _≡₁_ ⦄
    where

    record IsEquality₂ (_≣_ : ≣-Type') : Set (ℓ-suc ℓ₁) where
      constructor eq
      field
        ≣-≡-≡ : ∀ {x y} → let
          x≡y : Type ℓ₁
          x≡y = x ≡₁ y

@@

    module _
      (_≡₂_ : ≣-Type')
      ⦃ eq₂ : IsEquality _≡₂_ ⦄
      where

@@

      record IsEquality₃ (_≣_ : ≣-Type') : Set (ℓ-suc ℓ₁) where
        constructor eq
        field
          ≣-≡-≡ : ∀ {x y} → let
            x≡y : Type ℓ₁
            x≡y = x ≡₁ y

@@

      module _
        (_≡₂_ : ≣-Type')
        ⦃ eq₂ : IsEquality _≡₂_ ⦄
        where

        instance
          ≡₂-Equality₃ : IsEquality₃ _≡₂_
          ≡₂-Equality₃ = eq α
            where
              open IsEquality eq₃
              α : ∀ {x y} → (x ≡₂ y) ≡₃ (x ≡₁ y)
              α = transport ≡-≡-≣ (IsEquality₂.≣-≡-≡ (≡₂-Equality₂ _≡₂_))

      module _ {_≣_ : ≣-Type'} where
        sym-Equality₃ : (≡-≡-≣ : {x y : A} → let
          x≡y : Type (ℓ-max a ℓ)
          x≡y = x ≡₁ y
          x≣y = x ≣ y
          in x≡y ≡₃ x≣y)
          → IsEquality₃ _≣_
        sym-Equality₃ ≡-≡-≣ = eq (let
          α₁ = IsEquality.≡-≡-≣ eq₃
          α₂ = transport (sym α₁) ≡-≡-≣
          in transport α₁ (sym α₂))
\end{code}
